\documentclass[aspectratio=169, 10pt]{beamer}
\usetheme{Madrid}
\usecolortheme{whale}
\usepackage{graphicx}
\usepackage{booktabs}
\usepackage{amssymb}
\usepackage[utf8]{inputenc}

% Settings
\setbeamertemplate{navigation symbols}{}
\setbeamertemplate{itemize items}[circle]

\title[MediSim Iteration]{MediSim: Phase 3 Progress \& Delivery}
\subtitle{Multimodal Diagnostics \& Agentic Triage}
\author[Phase 3 Team]{Natural Language Processing Group Project}
\institute[AIT]{Asian Institute of Technology}
\date{\today}

\begin{document}

\begin{frame}
    \titlepage
\end{frame}

\begin{frame}{1. Background \& The Operational Gap}
    \textbf{The Clinical Dilemma:}
    \begin{itemize}
        \item Global hospital systems face unprecedented patient routing congestion and limited triage staffing.
        \item Legacy vision models process isolated radiology files (Unimodal) without interrogating the patient.
        \item Generative LLMs converse extremely well but lack explicit, mathematically bounded medical context, actively leading to critical clinical hallucinations.
    \end{itemize}
    \vspace{0.5cm}
    \textbf{The MediSim Objective:}
    \begin{quote}
        Can integrating a strictly deterministic Multimodal Vision-Language pipeline directly inside an LLM Multi-Agent conversational framework safely regulate diagnostic capabilities while preventing subjective hallucinations?
    \end{quote}
\end{frame}

\begin{frame}{2. Independent \& Dependent Evaluation Variables}
    \textbf{Experimental Protocol Design:}
    We evaluate the framework utilizing a rigid \textit{Within-Subjects} HCI approach running against the verified IU X-Ray clinical dataset baseline ($N=2,771$ patient arrays). \\
    \vspace{0.4cm}
    \begin{columns}
        \column{0.45\textwidth}
        \textbf{Independent Variables (IV):}
        \begin{itemize}
            \item \textbf{A:} Traditional Unimodal Baseline (ResNet-18 only)
            \item \textbf{B:} Full Multimodal Fusion (ResNet-18 + Bio\_ClinicalBERT)
        \end{itemize}
        
        \column{0.45\textwidth}
        \textbf{Dependent Variables (DV):}
        \begin{itemize}
            \item Macro F1-Score (Addressing clinical class imbalances).
            \item Frequency of hallucinated contraindications during Triage testing.
        \end{itemize}
    \end{columns}
\end{frame}

\begin{frame}{3. Deterministic Pipeline: The Multimodal Nexus}
    \textbf{Architecture Breakdown:}
    \begin{itemize}
        \item \textbf{Visual Mapping:} ResNet-18 CNN drops chest X-rays onto a $D_V=128$ dimensional plane.
        \item \textbf{Subjective Tokenization:} Migrated away from deprecated biLSTM structures toward the \textbf{Bio\_ClinicalBERT Hugging Face Transformer}. It forces subjective patient symptoms through massive $D=768$ dimension contextual mapping before dimension-reducing to $D_T=128$.
        \item \textbf{Softmax Fusion:} The physical visual signals and the conceptual textual signals merge into unified probability tensors mapped to 15 pulmonary pathology classifiers.
    \end{itemize}
\end{frame}

\begin{frame}{4. Interactive Pipeline: Multi-Agent Clinical Triage}
    Rather than unleashing a single unified LLM, we implemented a partitioned generative orchestration using LangChain bridging API calls to Gemini 2.5 Flash.
    \vspace{0.3cm}
    \begin{enumerate}
        \item \textbf{The Triage Nurse:} A high-empathy listener deployed exclusively for compassionate data intake and psychological de-escalation prior to analysis.
        \item \textbf{The Specialist Doctor:} A strict, rigid analytical mind ingesting the deterministic pipeline probabilities and producing targeted diagnosis theories.
        \item \textbf{The RAG Fact-Checker:} Operates completely behind the scenes querying Google Firestore structures to explicitly verify no proposed treatments violate user-recorded chronic contraindications!
    \end{enumerate}
\end{frame}

\begin{frame}{5. Empirical Results \& Testing Capabilities}
    \textbf{Multimodal Performance Verification:}
    \begin{table}[]
        \centering
        \begin{tabular}{r c c}
            \toprule
            \textbf{Pipeline Configuration} & \textbf{Top-1 Accuracy} & \textbf{Macro F1-Score} \\
            \midrule
            Baseline Unimodal (ResNet-18) & 46.04\% & 41.25\% \\
            \textbf{Multimodal Fusion Framework} & \textbf{51.08\%} & \textbf{46.82\%} \\
            \bottomrule
        \end{tabular}
    \end{table}
    \vspace{0.3cm}
    \textit{Insight:} We achieved a verified +5.04\% qualitative leap mathematically by coupling symptom semantics exclusively to the Chest X-Ray matrices. 
\end{frame}

\begin{frame}{6. Hallucination Interception}
    \textbf{System Security Outcomes:}
    During iterative conversational testing, the introduction of the independent \textit{Fact-Checker} agent yielded a $\sim 0\%$ unflagged hallucination rate against contraindications. 
    \begin{itemize}
        \item If a user presents severe asthma in their Firestore EMR matrix and the generative Specialist suggests a detrimental prescription interactively... 
        \item The Fact-Checker strictly intersects the workflow network and aggressively fires an emergency Fallback screen across the React dashboard automatically warning the patient!
    \end{itemize}
\end{frame}

\begin{frame}{7. Phase 4 Target Trajectory}
    \textbf{Next Logical Steps:}
    \begin{itemize}
        \item \textbf{Clinical User Trials:} Employing formal HCI Evaluation methodologies capturing empirical UI trust utilizing explicit SUS indexing structures against Multimodal vs. Unimodal platforms.
        \item \textbf{System Logging Tracker:} Incorporating continuous Weights \& Biases (\texttt{WandB}) structures to physically track network mapping telemetry natively across iteration pipelines.
    \end{itemize}
    \vspace{0.5cm}
    \centering \textbf{Thank You.} \\
    \textit{Preparing for Live Application Demonstration...}
\end{frame}

\end{document}
